Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage

### 2022-08-31 paper/paper.tex
add GRF
add Agent class to be the superclass of class UAV_AGENTmodel.m and Robot.m. oneUAV traj stable. Change the structure of setting sys, sys_a, sys_s.

The external disturbances during tracking control must also be considered. The agent ...
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

Fault-tolerant contrl (FTC) ...

@@

\textit{robot:} \begin{enumerate}
    \item system parameters: Appendix E in \cite{ourrobot}
    \item designed parameters:
\end{enumerate}

The tracking error and fault signal estimation of UAV $\alpha_{1,1}$ are shown in Fig. \ref{fig:UAV, error, estimation}, where the external disturbances is set to... . The tracking error and error signal estimation of the robot $\alpha_{1,2}$ are shown in Fig. \ref{fig:robot, error, estimation}, where the external disturbances is set to... .
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:UAV, error, estimation}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of robot walking.}%
    \label{fig:robot, error, estimation}
\end{figure}

>>>>

In order to cope with the fault in the actual system, the fault-tolerant control (FTC) has also been widely studied. According to the way of handling the fault, it can be divided into the passive FTC and the active FTC \cite{6669235}. The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it. In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller. Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

@@

\textit{robot:} \begin{enumerate}
    \item system parameters: Appendix E in \cite{ourrobot}
    \item designed parameters: $Q_1=,Q_2=,R=,rho=$ % correspond to x - xr, R=, \rho=$
\end{enumerate}

For convenience, the distubance $d_1(t)$ in actuator fault is set as $d_1(t)=0.2\cos(t)$ and the sensor fault is set as $f_2(t)=\sin(t)$. The tracking error and fault signal estimation of UAV $\alpha_{1,1}$ are shown in Fig. \ref{fig:UAV, error, estimation}. The tracking error and error signal estimation of the robot $\alpha_{1,2}$ are shown in Fig. \ref{fig:robot, error, estimation}.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
    \label{fig:UAV, error, estimation}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of robot walking.}%
    \label{fig:robot, error, estimation}
\end{figure}
